---
title: "practice"
author: "Emma"
date: "2026-09-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Section 0: library 
Command, option, I to make new code chunk 
```{r message=FALSE,echo=FALSE}
library(tidyverse)
```

# Section 1: generating a sample, running a mean 
```{r}
sample = rnorm(600)
```
I just made a sample, and the mean is `r mean(sample)` 

# Section 2: making a new data frame 

```{r}
new_df=
  tibble(
    x = rnorm(600, sd = 0.5),
    y = 1 + 2 * x + rnorm(600)
  )

tail(new_df)
```
# Section 3: I'm gonna make a plot! 

```{r}
ggplot(new_df, aes(x = x)) + geom_histogram()
```

The mean of this new histogram is `r round(mean(pull(new_df, x)), 2)`

# Section 4: Writing Fun 
## It is kind of fun 
### Actually 
*Now I'm just going to write a bit* **And this part is gonna be in bold** Or will it be `code`. 
I can write superscripts^2^ or subscripts~2~

* I like lists 
* I really do 
  * I wish 
  * I could write a haiku 


